### 2024-08-18 paper.tex
proof of 2

    There are three things to check: (1) the chains are no longer than their claimed lengths, (2) the claimed lengths sum to \(m\), and (3) the span of the chains is \(\mathbb{C}^m\).

@@

>>>>

    There are three things to check: (1) the chains are no longer than their claimed lengths, (2) the claimed lengths sum to \(m + n\), and (3) the span of the chains is \(\mathbb{C}^{m + n}\).

@@

        The sum of the lengths is
        \[\sum_{i \notin I} (p_i + q_i) + (n + P) + \sum_{i \in I} (q_i + P_i).\]
        Writing \(I = \{i_1 < \cdots < i_{|I|}\}\), we note that \(P = p_{i_1}\), that \(P_{i_{|I|}} = 0\), and that for \(l < |I|\) we have \(P_{i_l} = p_{i_{l + 1}}\).
        Thus, the sum above is 
        \[\sum_{i \notin I} (p_i + q_i) + (n + p_{i_1}) + \sum_{l = 1}^{|I|} (q_{i_l} + p_{i_{l + 1}}) = \]
        \[\sum_{i \notin I} (p_i + q_i) + n + \sum_{l = 1}^{|I|} (q_{i_l} + p_{i_l}) = n + \sum_i (q_i + p_i) = m + n.\]
